Resource Adequacy and Operational Security Interaction in the EPOC 2030-50 Project

### 2022-11-23 papers/main.tex
Include comparison of Uliege model results

We begin by illustrating the tradeoff that exists between real time load shedding and day ahead reserve shedding with a simple model. No network or unit commitment constraints are included and no storage either. The latter choice is made since in this model formulation storage is not able to contribute to operating reserve requirements, complicating the interpretation of the results.

\subsection{Comparison with ULiege operational security results}

@@

@@

>>>>

We begin by illustrating the tradeoff that exists between real time load shedding and day ahead reserve shedding with a simple model. No network or unit commitment constraints are included and no storage either. The latter choice is made since in this model formulation storage is not able to contribute to operating reserve requirements, complicating the interpretation of the results. The results are shown in \figref{fig:simple_reserve_vs_load_shedding}.

\begin{figure}[h]
    \centering
    \begin{subfigure}[t]{0.9\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../plots/copperplate_adequacy_security_tradeoff/load_shedding_vs_reserve_shedding}
        \caption{Reserve shedding plotted as a function of load shedding}
    \end{subfigure}
    \begin{subfigure}[t]{0.9\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../plots/copperplate_adequacy_security_tradeoff/load_shedding_vs_expected_load_shedding}
        \caption{Expected additional real time load shedding (reserve shedding weighted by activation probability) plotted as a function of load shedding.}
    \end{subfigure}
\caption{Simple illustration of the potential trade-off between planned load shedding (i.e. day ahead adequacy) and expected load shedding (i.e. real time operational security). Results are for day 161, no storage, unit commitment or network constraints are included.\label{fig:simple_reserve_vs_load_shedding}}
\end{figure}

\figref{fig:simple_reserve_vs_load_shedding} is included here to illustrate the trade-off we wanted to be able to investigate. However, for the reasons described in \secref{sec:initial_results} and \bref{sec:ULiege_comparison}, this was not possible.

\subsection{Comparison with ULiege operational security results} \label{sec:ULiege_comparison}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[t]{0.9\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../plots/compare_ULiege_results/forecast_only_no_contingency.pdf}
        \caption{Day ahead load shedding for DUC-PR and operational security power flow model.}
    \end{subfigure}
    \begin{subfigure}[t]{0.9\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../plots/compare_ULiege_results/with_scenarios_no_contingency.pdf}
        \caption{Expected load shedding for DUC-PR and operational security power flow model.}
    \end{subfigure}
\caption{Results are for day 309, with storage, unit commitment and network (reserve activation) constraints.\label{fig:Uliege_compare}}
\end{figure}

@@

While the remark regarding storage could be resolved by allowing for storage to contribute to operating reserves as in \cite{Bruninx2016}, the remaining two issues are non-trivial to address in the DUC-PR framework. A stochastic unit commitment model, in which real time imbalances are fully defined within a scenario, would lend itself more easily to addressing these issues while coming at considerable computational cost.
